A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@

Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}. Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs. Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.

>>>>

Additionally, the number of \PN[1]{2} triangular element-pairs mesh resolution was reduced from $4112$ (BaseCase, Fig,~\ref{fig:HiRes_LowRes_Mesh}a) to $728$ (upscaled cases, Fig,~\ref{fig:HiRes_LowRes_Mesh}b), a reduction by a factor of approximately $5.6$.

@@
